---
title: "case6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(HLMdiag)
library(lme4)
library(nlme)
library(ggplot2)
library(nullabor)
library(ggforce)
library(dplyr)
library(stringr)
#library(mvtnorm)
```

Autism data has 155 children between the ages of 2 and 13 who were diagnosed with either autism spectrum disorder or non-spectrum developmental delays at age 2.

It contains 604 observations with 7 variables:

- `childid`: Child ID
- `sicdegp`: Sequenced Inventory of Communication Development group (an assessment of expressive language development) with levels low, mod, and high
- `age2`: Age (in years) centered arond age 2 (age at diagnosis)
- `vsae`: Vineland Socialization Age Equivalent
- `gender`: Child's gender, female and male
- `race`: Child's race, white and non-white
- `bestest2`: Diagnosis at age 2, autism and pdd

```{r}
data(autism)
str(autism)
summary(autism)
length(unique(autism$childid))
```


```{r}
names(gsummary(autism, form = ~childid, inv = T))
```

- subject-level variables:
+ `chilidid`
+ `sicdegp`
+ `gender`
+ `race`
+ `bestest2`

```{r}
ggplot(autism, aes(age2, log10(vsae))) + geom_point() + facet_wrap_paginate(~childid, nrow = 5, ncol = 5, page = 1) + geom_smooth(method = "lm", se = F)
```

- `age2` has the relative positive relationship with `vsae`
- It seems to have the similar intercept but with different slopes.

```{r}
ggplot(autism, aes(gender, vsae)) + geom_boxplot() + scale_y_log10()
```

- By plotting the `gender` versus `vsae`, there is no much difference between male and female with respective to `vsae`.

```{r}
ggplot(autism, aes(interaction(gender, race), vsae)) + geom_boxplot() + scale_y_log10()
```

- White has higher value in `vsae` than non-white on average
- Female has higher value in `vsae` than male on average

```{r}
ggplot(autism, aes(sicdegp, vsae, fill = race)) + geom_boxplot() + scale_y_log10()
```

- Positive relationship with `sicdegp` and `vsae` (higher level in `sicdegp` results in higher value in `vsae`)
- `race` for white seems to have higher value in `vsae`.

```{r}
ggplot(autism, aes(bestest2, vsae)) + geom_boxplot() + scale_y_log10()
```

- pdd seems to have higher value in `vsae` than autism

At this stage, the variables, interaction of `gender` and `race`, `sicdegp`, `age2` and `bestest2` include in the model as matrix of fixed effect. From the `age2` versus `vsae` plot, the intercept seems to be same while the slope is different for each different children. Then we treat the random effect with random slope. As Adam mentioned, the model for LMM needs the quadratic random slope.

```{r model}
colnames(autism)[4] <- c("y")
autism.mod <- lmer(y ~ age2 + sicdegp + gender:race + bestest2 + (age2 - 1|childid) + (I(age2^2)-1|childid), data = autism)
vc <- as.data.frame(VarCorr(autism.mod))
#vc$vcov[vc$grp == "childid.1"]
```

```{r fittedfn}
autism.extract.fitted.mod <- function(mod, data){
  n <- getME(mod, "n")
  child <- unique(data$childid)
  nchild <- length(child)
  
  y <- getME(mod, "y")
  X <- getME(mod, "X")
  beta <- getME(mod, "beta")
  Z <- getME(mod, "Z")
  u <- getME(mod, "b")
  q <- getME(mod, "q")
  
  vc <- as.data.frame(VarCorr(mod))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(mod) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(mod) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G

  fitted_df <- data %>% 
    dplyr::mutate(
      fitted = as.vector(X %*% beta),
      resm = y - fitted,
      resc = as.vector(y - fitted - Z %*% u),
      index = 1:n()) %>% 
    mutate(resm_std = resm/sqrt(diag(varMargRes)[index]),
           resc_std = resc/sqrt(diag(varCondRes)[index])) %>% 
    ungroup()
}
```

```{r lcrfn}
autism.extract.lcr.mod <- function(mod, data){
  n <- getME(mod, "n")
  child <- unique(data$childid)
  nchild <- length(child)
  
  y <- getME(mod, "y")
  X <- getME(mod, "X")
  beta <- getME(mod, "beta")
  Z <- getME(mod, "Z")
  u <- getME(mod, "b")
  q <- getME(mod, "q")
  
  vc <- as.data.frame(VarCorr(mod))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)

  Sigma <- Z %*% G %*% t(Z) + R 

  Sigma_inv <- solve(Sigma)

  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(mod) %*% t(X) %*% Sigma_inv

  varMargRes <- Sigma - X %*% vcov(mod) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted <-  as.vector(X %*% beta)
  resm <-  y - fitted
  resc <-  as.vector(y - fitted - Z %*% u)
  index <- 1:nrow(data)
  resm_std <-  resm/sqrt(diag(varMargRes)[index])
  resc_std = resc/sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))

  resmcp_sl <- tibble::tibble(resmcp)
  
  return(resmcp_sl)
}
```

```{r simulatefn}
autism.sim <- function(mod, data, nsim = 19, seed, std = FALSE){
  fit.sim <- simulate(mod, nsim = nsim, seed = seed, std = std)
  fit.refit <- lapply(fit.sim, refit, object = mod)
  fit.simy <- lapply(fit.refit, function(x) getME(x, 'y'))
  fit.simy.y <- do.call("cbind", fit.simy)
  fit.simy.y <- reshape2::melt(fit.simy.y)[-1]
  names(fit.simy.y) <- c(".n", "y")
  fit.simy.y$.n <- as.numeric(str_extract(fit.simy.y$.n, "\\d+"))
  fit.simy.y$age2 <- rep(data$age2, 19)
  fit.simy.y$sicdegp <- rep(data$sicdegp, 19)
  fit.simy.y$gender <- rep(data$gender, 19)
  fit.simy.y$race <- rep(data$race, 19)
  fit.simy.y$bestest2 <- rep(data$bestest2, 19)
  fit.simy.y$childid <- rep(data$childid, 19)
  return(fit.simy.y)
}
```

# Data plots

```{r datas}
autism.fitted <- autism.extract.fitted.mod(autism.mod, autism)
autism.lcr <- autism.extract.lcr.mod(autism.mod, autism)
```


```{r}
ggplot(autism.fitted, aes(index, resm_std, color = gender, shape = race)) + 
  geom_point() + 
  geom_text(
    data = autism.fitted %>% 
      filter(resm_std > 5), 
    aes(label = index), 
    nudge_x = 0.35, nudge_y = 0.35, 
    size = 2)
ggplot(autism.fitted, aes(index, resc_std, color = gender, shape = race)) + geom_point()
ggplot(autism.fitted, aes(sample = resc_std)) + geom_qq() + geom_qq_line(color = "red")
ggplot(autism.lcr, aes(sample = resmcp)) + geom_qq() + geom_qq_line(color = "red")
```

- the outlying observations are more allocated in the female with non-white feature
- the conditional residuals do not follow a normal distribution while the least confounded conditional residual does not follow a normal distribution as well.

# *Version 1

Simulate from the true model:

```{r}
set.seed(1234)
vc <- VarCorr(autism.mod)
G <- as.matrix(bdiag(vc))
sig.G <- sqrt(G)
sig.e <- sigma(autism.mod)

n <- getME(autism.mod, "n")
q <- getME(autism.mod, "q")
m <- q/nrow(G)

# normal error
e <- rnorm(n = n, mean = 0, sd = sig.e)

# normal random effects
b <- mvrnorm(n = m, mu = rep(0,2), Sigma = G)
bvec <- c(b[,1], b[,2])

y <- as.vector(getME(autism.mod, "X") %*% fixef(autism.mod) + getME(autism.mod, "Z") %*% bvec + e)

v1.autism <- tibble(autism[,-4], y)
```

```{r}
a.v1.mod <- lmer(y ~ age2 + sicdegp + gender:race + bestest2 + (age2 - 1|childid) + (I(age2^2)-1|childid), data = v1.autism)
```

```{r}
v1.fitted <- autism.extract.fitted.mod(a.v1.mod, v1.autism)
v1.lcr <- autism.extract.lcr.mod(a.v1.mod, v1.autism)
```

# Data plots

```{r}
sl_mr <- ggplot(v1.fitted, aes(index, resm_std, color = gender, shape = race)) + geom_point(alpha = 0.8) + geom_hline(yintercept = 0) + xlab("Observation Index") + ylab("Stadardised Marginal Residuals") +theme()

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/second_presentation/plots/sl_mr.png", plot = sl_mr, device = "png", dpi = 300)
ggplot(v1.fitted, aes(index, resc_std, color = gender, shape = race)) + geom_point() + geom_hline(yintercept = 0)
ggplot(v1.fitted, aes(sample = resc_std)) + geom_qq() + geom_qq_line(color = "red") 
ggplot(v1.lcr, aes(sample = resmcp)) + geom_qq() + geom_qq_line()
```

- From the simulated data set, the conditional residuals fit better in normal distribution than the least confounded residuals. It looks like that has less outlying observations. Although, the observations who is female with non-white still can be treated as outliers on the top in the marginal residuals.

## 1st replication

```{r v11.sim}
autism.v11.sim <- autism.sim(a.v1.mod, v1.autism, seed = 1724)
```

```{r v11n.fitted}
autism.v11n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v11.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v11n.lcr}
autism.v11n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v11.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)

  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
lineup(true = v1.fitted, samples = autism.v11n.fitted, pos = 7) %>%
  ggplot(aes(index, resm_std, color = gender, shape = race)) + geom_point() +
  facet_wrap(~.sample, ncol = 5) + theme(axis.title = element_blank(), axis.text = element_blank())
```

```{r}
a11.1 <- lineup(true = v1.fitted, samples = autism.v11n.fitted, pos = 7) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() + facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none")

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v11_M_7.png", 
  plot = a11.1, device = "png", dpi = 300,
  height = 12, width = 12)
```


```{r}
a11.2 <- lineup(true = v1.fitted, samples = autism.v11n.fitted, pos = 7) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none")

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v11_C_7.png", 
  plot = a11.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a11.3 <- lineup(true = v1.fitted, samples = autism.v11n.fitted, pos = 9) %>%
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v11_CN_9.png",
       plot = a11.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a11.4 <- lineup(true = v1.lcr, samples = autism.v11n.lcr, pos = 9) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v11_LN_9.png",
       plot = a11.4, device = "png", dpi = 300, height = 12, width = 12)
```

## 2nd replication

```{r v12.sim}
autism.v12.sim <- autism.sim(a.v1.mod, v1.autism, seed = 7620)
```

```{r v12n.fitted}
autism.v12n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v12.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v12n.lcr}
autism.v12n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v12.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a12.1 <- lineup(true = v1.fitted, samples = autism.v12n.fitted, pos = 7) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v12_M_7.png", 
  plot = a12.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a12.2 <- lineup(true = v1.fitted, samples = autism.v12n.fitted, pos = 7) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v12_C_7.png", 
  plot = a12.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a12.3 <- lineup(true = v1.fitted, samples = autism.v12n.fitted, pos = 9) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v12_CN_9.png",
       plot = a12.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a12.4 <- lineup(true = v1.lcr, samples = autism.v12n.lcr, pos = 9) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v12_LN_9.png",
       plot = a12.4, device = "png", dpi = 300, height = 12, width = 12)
```

## 3rd replication

```{r v13.sim}
autism.v13.sim <- autism.sim(a.v1.mod, v1.autism, seed = 2746)
```

```{r v13n.fitted}
autism.v13n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v13.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v13n.lcr}
autism.v13n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v13.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a13.1 <- lineup(true = v1.fitted, samples = autism.v13n.fitted, pos = 13) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v13_M_13.png", 
  plot = a13.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a13.2 <- lineup(true = v1.fitted, samples = autism.v13n.fitted, pos = 13) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v13_C_13.png", 
  plot = a13.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a13.3 <- lineup(true = v1.fitted, samples = autism.v13n.fitted, pos = 4) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v13_CN_4.png",
       plot = a13.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a13.4 <- lineup(true = v1.lcr, samples = autism.v13n.lcr, pos = 4) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v13_LN_4.png",
       plot = a13.4, device = "png", dpi = 300, height = 12, width = 12)
```


## 4th replication

```{r v14.sim}
autism.v14.sim <- autism.sim(a.v1.mod, v1.autism, seed = 8502)
```

```{r v14n.fitted}
autism.v14n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v14.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v13n.lcr}
autism.v14n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v14.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a14.1 <- lineup(true = v1.fitted, samples = autism.v14n.fitted, pos = 13) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v14_M_13.png", 
  plot = a14.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a14.2 <- lineup(true = v1.fitted, samples = autism.v14n.fitted, pos = 13) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v14_C_13.png", 
  plot = a14.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a14.3 <- lineup(true = v1.fitted, samples = autism.v14n.fitted, pos = 4) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v14_CN_4.png",
       plot = a14.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a14.4 <- lineup(true = v1.lcr, samples = autism.v14n.lcr, pos = 4) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5)+
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v14_LN_4.png",
       plot = a14.4, device = "png", dpi = 300, height = 12, width = 12)
```

# *Version 2

We added the error term as student t distributed.

```{r}
set.seed(5692)
## t distribution
e  <- rt(n = n, ncp = sig.e, df = 15)
y <- as.vector(getME(autism.mod, "X") %*% fixef(autism.mod) + getME(autism.mod, "Z") %*% bvec + e)

autism.repc2 <- tibble(autism[,-4], y)
a.v2.mod <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) -1 |childid), data = autism.repc2)
```

```{r}
a.v2.fitted <- autism.extract.fitted.mod(a.v2.mod, autism.repc2)
a.v2.lcr <- autism.extract.lcr.mod(a.v2.mod, autism.repc2)
```

# Data plots

```{r}
ggplot(a.v2.fitted, aes(index, resm_std, color = gender, shape = race)) + geom_point()
ggplot(a.v2.fitted, aes(index, resc_std, color = gender, shape = race)) + geom_point()
ggplot(a.v2.fitted, aes(sample = resc_std)) + geom_qq() + geom_qq_line(color = "red")
ggplot(a.v2.lcr, aes(sample = resmcp)) + geom_qq() + geom_qq_line(color = "red")
```

- The outlying observations can be detected as the non-white female in the marginal residuals but more with non-white males are detected in the conditional residuals
- Both conditional residual and least confounded residual are less normally distributed compared with version 1.

## 1st replication

```{r v21.sim}
autism.v21.sim <- autism.sim(a.v2.mod, autism.repc2, seed = 1234)
```

```{r v21n.fitted}
autism.v21n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v21.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v21n.lcr}
autism.v21n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v21.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a21.1 <- lineup(true = a.v2.fitted, samples = autism.v21n.fitted, pos = 5) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v21_M_5.png", 
  plot = a21.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a21.2 <- lineup(true = a.v2.fitted, samples = autism.v21n.fitted, pos = 5) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5)+
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v21_C_5.png", 
  plot = a21.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a21.3 <- lineup(true = a.v2.fitted, samples = autism.v21n.fitted, pos = 8) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5)+ 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v21_CN_8.png",
       plot = a21.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a21.4 <- lineup(true = a.v2.lcr, samples = autism.v21n.lcr, pos = 8) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v21_LN_8.png",
       plot = a21.4, device = "png", dpi = 300, height = 12, width = 12)
```

## 2st replication

```{r v22.sim}
autism.v22.sim <- autism.sim(a.v2.mod, autism.repc2, seed = 7620)
```

```{r v22n.fitted}
autism.v22n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v22.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v22n.lcr}
autism.v22n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v22.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a22.1 <- lineup(true = a.v2.fitted, samples = autism.v22n.fitted, pos = 5) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5)+
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v22_M_5.png", 
  plot = a22.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a22.2 <- lineup(true = a.v2.fitted, samples = autism.v22n.fitted, pos = 5) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5)+
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v22_C_5.png", 
  plot = a22.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a22.3 <- lineup(true = a.v2.fitted, samples = autism.v22n.fitted, pos = 8) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v22_CN_8.png",
       plot = a22.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a22.4 <- lineup(true = a.v2.lcr, samples = autism.v22n.lcr, pos = 8) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5)+ 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v22_LN_8.png",
       plot = a22.4, device = "png", dpi = 300, height = 12, width = 12)
```

## 3rd replication

```{r v23.sim}
autism.v23.sim <- autism.sim(a.v2.mod, autism.repc2, seed = 4739)
```

```{r v23n.fitted}
autism.v23n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v23.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v22n.lcr}
autism.v23n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v23.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a23.1 <- lineup(true = a.v2.fitted, samples = autism.v23n.fitted, pos = 15) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5)+
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v23_M_15.png", 
  plot = a23.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a23.2 <- lineup(true = a.v2.fitted, samples = autism.v23n.fitted, pos = 15) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5)+
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v23_C_15.png", 
  plot = a23.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a23.3 <- lineup(true = a.v2.fitted, samples = autism.v23n.fitted, pos = 20) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v23_CN_20.png",
       plot = a23.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a23.4 <- lineup(true = a.v2.lcr, samples = autism.v23n.lcr, pos = 20) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v23_LN_20.png",
       plot = a23.4, device = "png", dpi = 300, height = 12, width = 12)
```

## 4th replication

```{r v24.sim}
autism.v24.sim <- autism.sim(a.v2.mod, autism.repc2, seed = 8502)
```

```{r v24n.fitted}
autism.v24n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v24.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v24n.lcr}
autism.v24n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v24.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a24.1 <- lineup(true = a.v2.fitted, samples = autism.v24n.fitted, pos = 15) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v24_M_15.png", 
  plot = a24.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a24.2 <- lineup(true = a.v2.fitted, samples = autism.v24n.fitted, pos = 15) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5)+
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v24_C_15.png", 
  plot = a24.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a24.3 <- lineup(true = a.v2.fitted, samples = autism.v24n.fitted, pos = 20) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5)+ 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v24_CN_20.png",
       plot = a24.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a24.4 <- lineup(true = a.v2.lcr, samples = autism.v24n.lcr, pos = 20) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5)+ 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v24_LN_20.png",
       plot = a24.4, device = "png", dpi = 300, height = 12, width = 12)
```

- The data plot of least confounded residual is hard to be identified.

# *Version 3

```{r}
autism %>% group_by(childid) %>% summarise(mean = mean(y))

mean(autism$y)
```

```{r}
set.seed(2639)
ind <- sample(604, 120, replace = F)
autism.repc3 <- autism
autism.repc3[ind,]$y <- autism.repc3[ind,]$y + median(autism.repc3$y) * 0.2
```

```{r}
a.v3.mod <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) -1 |childid), data = autism.repc3)
```

```{r}
a.v3.fitted <- autism.extract.fitted.mod(a.v3.mod, autism.repc3)
a.v3.lcr <- autism.extract.lcr.mod(a.v3.mod, autism.repc3)
```

# Data plots

```{r}
ggplot(a.v3.fitted, aes(index, resm_std, color = gender, shape = race)) + geom_point()

aut_dp2 <- ggplot(a.v3.fitted, aes(interaction(gender, race), resc_std)) + geom_boxplot() + ylab("Standardised conditional residuals") + theme()
ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/second_presentation/aut_dp2.png", plot = aut_dp2, device = "png", dpi = 300)

ggplot(a.v3.fitted, aes(sample = resc_std)) + geom_qq() + geom_qq_line(color = "red")

ggplot(a.v3.lcr, aes(sample = resmcp)) + geom_qq() + geom_qq_line(color = "red")
```

- With version 3, there are more outliers on the both marginal residual and conditional residuals. While, conditional residual may works better on detecting the outlying observations.
- Both conditional residual and least confounded residual are not normally distributed as the tails on both side for conditional residual and the tails on the bottom for least confounded residual.

## 1st replication

```{r}
autism.v31.sim <- autism.sim(a.v3.mod, autism.repc3, seed = 1234)
```

```{r v31n.fitted}
autism.v31n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v31.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v31n.lcr}
autism.v31n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v31.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a31.1 <- lineup(true = a.v3.fitted, samples = autism.v31n.fitted, pos = 15) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v31_M_15.png", 
  plot = a31.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a31.2 <- lineup(true = a.v3.fitted, samples = autism.v31n.fitted, pos = 15) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v31_C_15.png", 
  plot = a31.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

- Outlying observations can be detected on both conditional and marginal residuals

### Normality checking

```{r}
a31.3 <- lineup(true = a.v3.fitted, samples = autism.v31n.fitted, pos = 11) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v31_CN_11.png",
       plot = a31.3, device = "png", dpi = 300, height = 12, width = 12)
```

- The data plot can be identified immediately.

```{r}
a31.4 <- lineup(true = a.v3.lcr, samples = autism.v31n.lcr, pos = 11) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v31_LN_11.png",
       plot = a31.4, device = "png", dpi = 300, height = 12, width = 12)
```

- The least confounded residual for the data plot can be detected as well as the outlier on the lower bottom.

## 2nd replication

```{r}
autism.v32.sim <- autism.sim(a.v3.mod, autism.repc3, seed = 7620)
```

```{r v32n.fitted}
autism.v32n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v32.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v32n.lcr}
autism.v32n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v32.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a32.1 <- lineup(true = a.v3.fitted, samples = autism.v32n.fitted, pos = 15) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5)+
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v32_M_15.png", 
  plot = a32.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a32.2 <- lineup(true = a.v3.fitted, samples = autism.v32n.fitted, pos = 15) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v32_C_15.png", 
  plot = a32.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a32.3 <- lineup(true = a.v3.fitted, samples = autism.v32n.fitted, pos = 11) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v32_CN_11.png",
       plot = a32.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a32.4 <- lineup(true = a.v3.lcr, samples = autism.v32n.lcr, pos = 11) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v32_LN_11.png",
       plot = a32.4, device = "png", dpi = 300, height = 12, width = 12)
```

## 3rd replication

```{r}
autism.v33.sim <- autism.sim(a.v3.mod, autism.repc3, seed = 4739)
```

```{r v33n.fitted}
autism.v33n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v33.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v33n.lcr}
autism.v33n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v33.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a33.1 <- lineup(true = a.v3.fitted, samples = autism.v33n.fitted, pos = 2) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v33_M_2.png", 
  plot = a33.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a33.2 <- lineup(true = a.v3.fitted, samples = autism.v33n.fitted, pos = 2) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v33_C_2.png", 
  plot = a33.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a33.3 <- lineup(true = a.v3.fitted, samples = autism.v33n.fitted, pos = 6) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v33_CN_6.png",
       plot = a33.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a33.4 <- lineup(true = a.v3.lcr, samples = autism.v33n.lcr, pos = 6) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v33_LN_6.png",
       plot = a33.4, device = "png", dpi = 300, height = 12, width = 12)
```

## 4th replication

```{r}
autism.v34.sim <- autism.sim(a.v3.mod, autism.repc3, seed = 8502)
```

```{r v34n.fitted}
autism.v34n.fitted <- purrr::map_dfr(1:19, function(i){
  df <- autism.v34.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r v34n.lcr}
autism.v34n.lcr <- purrr::map_dfr(1:19, function(i){
  df <- autism.v34.sim %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1|childid) + (I(age2^2) - 1 | childid), data = df)
  
  n <- getME(m, "n")
  child <- unique(df$childid)
  nchild <- length(child)
  
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")
  
  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == "Residual"] * diag(n)
  G1 <- vc$vcov[vc$grp == "childid"] * diag(nchild)
  G2 <- vc$vcov[vc$grp == "childid.1"] * diag(nchild)
  G <- Matrix::bdiag(G1, G2)
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv 
  
  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(n-p)])))) %*% t(auxqn$vectors[1:n,1:(n-p)]) %*% solve(expm::sqrtm(R[1:n,1:n]))

  var.resmcp <- lt %*% varCondRes[1:n,1:n] %*% t(lt)

  resmcp <- (lt %*% resc[1:n] )/sqrt(diag(var.resmcp))
  
  .n = i

  tibble::tibble(.n, resmcp)
})
```

### Outlying observations

```{r}
a34.1 <- lineup(true = a.v3.fitted, samples = autism.v34n.fitted, pos = 2) %>%
  ggplot(aes(interaction(gender, race), resm_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v34_M_2.png", 
  plot = a34.1, device = "png", dpi = 300,
  height = 12, width = 12)
```

```{r}
a34.2 <- lineup(true = a.v3.fitted, samples = autism.v34n.fitted, pos = 2) %>%
  ggplot(aes(interaction(gender, race), resc_std)) + geom_boxplot() +
  facet_wrap(~.sample, ncol = 5) +
  ylab(NULL) + xlab(NULL) + 
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank())

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v34_C_2.png", 
  plot = a34.2, device = "png", dpi = 300,
  height = 12, width = 12)
```

### Normality checking

```{r}
a34.3 <- lineup(true = a.v3.fitted, samples = autism.v34n.fitted, pos = 6) %>% 
  ggplot(aes(sample = resc_std)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v34_CN_6.png",
       plot = a34.3, device = "png", dpi = 300, height = 12, width = 12)
```

```{r}
a34.4 <- lineup(true = a.v3.lcr, samples = autism.v34n.lcr, pos = 6) %>% 
  ggplot(aes(sample = resmcp)) + geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5) + 
  ylab(NULL) + xlab(NULL) +
  theme(axis.text.y = element_blank(), axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), axis.ticks.y = element_blank(), 
        legend.position="none", aspect.ratio = 1)

ggsave(filename = "~/Desktop/Masters/Master_Econometrics/S2 2020/ETF5550/master/figures/lineups/aut_v34_LN_6.png",
       plot = a34.4, device = "png", dpi = 300, height = 12, width = 12)
```



