---
title: "case4: Exercise Histories of Eating-Disordered and Control Subjects"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
library(car) # load the Blackmoor data
library(ggplot2)
library(skimr)
library(lme4)
library(dplyr)
library(tidyr)
library(purrr)
library(nullabor)
library(ggforce)
library(nlme)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE#,
  #cache.path = "cache/",
  #cache = TRUE
)
```

There are 945 observations with 231 subjects that contains patients' age and the amount of exercise expressed as estimated hours per week with 2 groups (control and patient). There are 112 observations that has zero value on exercise some are from the beginning and some are from the end. And 73 observations among them are from the patient group and the rest are from the control group.

```{r data}
data("Blackmore")
head(Blackmore)
skimr::skim(Blackmore)
#Blackmore <- Blackmore[!Blackmore$exercise == 0,]
Blackmore$log.exercise <- log(Blackmore$exercise + 5/60, 2)
Blackmore$age <- as.integer(Blackmore$age)
length(unique(Blackmore$subject))
```

There are 93 unqiue subjects in the control group. And there are 359 observations in the control group.

```{r control-data}
control <- Blackmore[Blackmore$group == "control",]
nrow(control)
skimr::skim(control)
length(unique(control$subject))
control.id<- unique(control$subject)
```


```{r age-log.exercise}
ggplot(Blackmore, aes(age, log.exercise, color = group)) + 
  geom_point() + 
  facet_wrap_paginate(~ subject, nrow = 5, ncol = 5, page = 8) + 
  geom_smooth(method = "lm", se = F)
```


```{r}
ggplot(Blackmore, aes(group, log.exercise)) + geom_boxplot() + geom_beeswarm()
```


From the plot we can see that the intercept and slope for different subjects are different.

## Model 1

```{r}
fit <- lmer(log.exercise ~ age*group  + (age + I(age^2)|subject), data = Blackmore)

summary(fit)
```

```{r}
all(getME(fit, "X") == model.matrix(~ age*group, data = Blackmore))
all(getME(fit, "Z") == model.matrix(~ -1 + subject:age + subject, data = Blackmore))
all(getME(fit, "y") == Blackmore$log.exercise)
```


```{r}
bl.extract.fitted.mod <- function(mod, data){
  N <- getME(mod, "n")
  subjects <- unique(data$subject)
  
  y <- getME(mod, "y")
  X <- model.matrix(~ age*group, data = Blackmore)
  beta <- fixef(fit)
  Z <- model.matrix(~ -1 + subject + subject:age, data = Blackmore)
  u <- c(ranef(mod)$subject[,1], ranef(mod)$subject[,2])
  q <- getME(mod, "q")
  
  vc <- as.data.frame(VarCorr(fit))
  R <- vc$vcov[vc$grp == 'Residual'] * diag(N)
  G1 <- vc$vcov[vc$grp == 'subject'][1] * diag(q/2)
  G2 <- vc$vcov[vc$grp == 'subject'][2] * diag(q/2)
  #G3 <- vc$vcov[vc$grp == 'subject'][3] * diag(q/3)
  G <- Matrix::bdiag(G1, G2)
  G[lower.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]
  G[upper.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]
  
  #G[232:462, 1:231] <- vc$vcov[vc$grp == 'subject'][4]
  #G[1:231, 232:462] <- vc$vcov[vc$grp == 'subject'][4]
  #G[463:693, 1:231] <- vc$vcov[vc$grp == 'subject'][5]
  #G[1:231, 463:693] <- vc$vcov[vc$grp == 'subject'][5]
  #G[463:693, 232:462] <- vc$vcov[vc$grp == 'subject'][6]
  #G[232:462, 463:693] <- vc$vcov[vc$grp == 'subject'][6]
  
  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)
  
  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(fit) %*% t(X) %*% Sigma_inv
  
  varMargRes <- Sigma - X %*% vcov(mod) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fit_bl <- data %>% 
    mutate(fitted = as.vector(X %*% beta),
           resm = y - fitted,
           resc = as.vector(y - fitted - Z %*% u),
           index = 1:n()) %>% 
    rowwise() %>% 
    mutate(resm_std = resm/sqrt(diag(varMargRes)[index]),
           resc_std = resc/sqrt(diag(varCondRes)[index])) %>% 
    ungroup()
}
```

```{r}
bl.extract.fitted.mod(fit, Blackmore)
```


### Plot 1
```{r}
ggplot(fit_bl, aes(fitted, resm_std)) + geom_point() + geom_hline(yintercept = 0)
```

### Plot 2
```{r}
ggplot(fit_bl, aes(index, resm_std)) + geom_point() + geom_hline(yintercept = 0)
```

### Plot 4
```{r}
ggplot(fit_bl, aes(index, resc_std)) + geom_point() + geom_hline(yintercept = 0)
```

### plot 5
```{r}
ggplot(fit_bl, aes(fitted, resc_std)) + geom_point() + geom_hline(yintercept = 0)
```

## Model 2 using the full data set

```{r}
data("Blackmore")
Blackmore$log.exercise <- log(Blackmore$exercise + 5/60, 2)
Blackmore$age <- as.integer(Blackmore$age)
```

```{r fit}
fit <- lmer(log.exercise ~ age*group  + (age + I(age^2)|subject), data = Blackmore)

summary(fit)
```

`vcov` is the covariance matrix of the fixed-effect estimates which is consistent with the mathmatical expression $V(\hat \beta) = (X^\top \Omega^{-1} X)^{-1}$ (`solve(t(X) %*% Sigma_inv %*% X)`).

Variance-covariance matrix of random effects $\mathbf G$, for example $2\times 2$ symmetric matrix:

\begin{bmatrix}
$g_1^2$ & $g_{12}^2$ \\
$g_{21}^2$ & $g__2^2$
\end{bmatrix}

Using `lower.tri` and `upper.tri` to apply the lower and upper triangular part of the matrix.
$G_1$ represents the variability of the intercept across subjects and $G_2$ refers the variablity of the slope of subjects. 

```{r model}
N <- nrow(Blackmore)
subjects <- unique(Blackmore$subject)

y <- Blackmore$log.exercise
X <- model.matrix(~ age*group, data = Blackmore)
beta <- fixef(fit)
Z <- model.matrix(~ -1 + subject + subject:age + subject:I(age^2), data = Blackmore)
u <- c(ranef(fit)$subject[,1], ranef(fit)$subject[,2], ranef(fit)$subject[,3])
q <- length(u)

vc <- as.data.frame(VarCorr(fit))
R <- vc$vcov[vc$grp == 'Residual'] * diag(N)
G1 <- vc$vcov[vc$grp == 'subject'][1] * diag(q/3)
G2 <- vc$vcov[vc$grp == 'subject'][2] * diag(q/3)
G3 <- vc$vcov[vc$grp == 'subject'][3] * diag(q/3)
G <- Matrix::bdiag(G1, G2, G3)
#G[lower.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]
#G[upper.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]

G[232:462, 1:231] <- vc$vcov[vc$grp == 'subject'][4]
G[1:231, 232:462] <- vc$vcov[vc$grp == 'subject'][4]
G[463:693, 1:231] <- vc$vcov[vc$grp == 'subject'][5]
G[1:231, 463:693] <- vc$vcov[vc$grp == 'subject'][5]
G[463:693, 232:462] <- vc$vcov[vc$grp == 'subject'][6]
G[232:462, 463:693] <- vc$vcov[vc$grp == 'subject'][6]

Sigma <- Z %*% G %*% t(Z) + R 
Sigma_inv <- solve(Sigma)

P <- Sigma_inv - Sigma_inv %*% X %*% vcov(fit) %*% t(X) %*% Sigma_inv

varMargRes <- Sigma - X %*% vcov(fit) %*% t(X) 
varCondRes <- R %*% P %*% R  
varU <- G - G %*% t(Z) %*% P %*% Z %*% G

fit_bl <- Blackmore %>% 
  mutate(fitted = as.vector(X %*% beta),
         resm = y - fitted,
         resc = as.vector(y - fitted - Z %*% u),
         index = 1:n()) %>% 
  rowwise() %>% 
  mutate(resm_std = resm/sqrt(diag(varMargRes)[index]),
         resc_std = resc/sqrt(diag(varCondRes)[index])) %>% 
  ungroup()

unit_bl <- expand_grid(subjects) %>% 
  mutate(Vi = map_dbl(subjects, ~{
    ind <- Blackmore %>% 
      mutate(index = 1:n()) %>% 
      filter(subject %in%  .x) %>% 
      pull(index)
    mi <- length(ind)
    Ei <- solve(expm::sqrtm(varMargRes[ind, ind])) %*% fit_bl$resm[ind]
    sqrt(sum((diag(mi) - Ei %*% t(Ei))^2)) / mi
  }),
  Mi = as.vector(t(u) %*% solve(varU) %*% u),
  index = 1:n())
```

### Least confounded conditional residual
```{r squart root of a matrix}
sqrt.matrix <- function(mat) {
                mat <- as.matrix(mat)
                singular_dec <- svd(mat,LINPACK = F)
                U <- singular_dec$u
                V <- singular_dec$v
                D <- diag(singular_dec$d)
                sqrtmatrix <- U %*% sqrt(D) %*% t(V)
        }
```

```{r}
#R.half <- sqrt.matrix(R)

R_half <- expm::sqrtm(R)

auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

p <- length(beta)

lt <- sqrt(solve(diag((auxqn$values[1:(N-p)])))) %*% t(auxqn$vectors[1:N,1:(N-p)]) %*% solve(expm::sqrtm(R[1:N,1:N]))

var.resmcp <- lt %*% varCondRes[1:N,1:N] %*% t(lt)

resmcp <- (lt %*% fit_bl$resc[1:N] )/sqrt(diag(var.resmcp))

resmcp.1 <- as.data.frame(resmcp)
```

#### QQ plot of the Standardised Least Confounded Conditional Residual

```{r}
ggplot(resmcp.1, aes(sample = V1)) + 
  geom_qq() + geom_qq_line(color = "red")
```



### Diagnostic Plot 1: Linearity of fixed effects

```{r}
ggplot(fit_bl, aes(fitted, resm_std)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

### Diagnostic Plot 2: Prescence of outlying observations

```{r}
ggplot(fit_bl, aes(index, resm_std)) + geom_point() + geom_hline(yintercept = 0)
```

### Diagnostic Plot 3: Within-units covariance matrix

```{r}
ggplot(unit_bl, aes(index, Vi)) + geom_point()+ xlab("Unit indicies") + ylab("Modified Lesaffre-Verbeke index")
```

### Diagnostic Plot 4: Prescense of outlying observations using conditional residual

- most different from the plot with the model `lmer(log.exercise ~ age*group  + (age|subject), data = Blackmore)` which refer to `fit2`.

```{r}
ggplot(fit_bl, aes(index, resc_std)) + geom_point() + geom_hline(yintercept = 0)
```

### Diagnostic Plot 5: Homoskedasticity of conditional errors 

```{r}
ggplot(fit_bl, aes(fitted, resc_std)) + geom_point() + geom_hline(yintercept = 0)
```

### Diagnostic Plot 6: Normality of conditional errors

```{r}
ggplot(fit_bl, aes(sample = resc_std)) + 
  geom_qq() + geom_qq_line(color = "red")
```

### Diagnostic Plot 7: Presencse of outlying subjects 

```{r}
ggplot(unit_bl, aes(index, Mi)) + geom_point() + xlab("Unit index") + ylab("Manhalanobis distance")
```

### Diagnostic Plot 8: Normality of the random effects

```{r}
ggplot(unit_bl, aes(sample = Mi)) + 
  geom_qq(distribution = stats::qchisq,
          dparams = list(df = q)) +
  geom_qq_line(color = "red",
               distribution = stats::qchisq,
               dparams = list(df = q))
```

## Model 3 without $age^2$ in random effect

```{r fit2-without age^2}
fit2 <- lmer(log.exercise ~ age*group  + (age|subject), data = Blackmore)

summary(fit2)
```

```{r}
X <- model.matrix(~ age*group, data = Blackmore)
beta <- fixef(fit2)
Z <- model.matrix(~ -1 + subject + subject:age, data = Blackmore)
u <- c(ranef(fit2)$subject[,1], ranef(fit2)$subject[,2])
q <- length(u)

vc <- as.data.frame(VarCorr(fit2))
R <- vc$vcov[vc$grp == 'Residual'] * diag(N)
G1 <- vc$vcov[vc$grp == 'subject'][1] * diag(q/2)
G2 <- vc$vcov[vc$grp == 'subject'][2] * diag(q/2)
#G3 <- vc$vcov[vc$grp == 'subject'][3] * diag(q/3)
G <- Matrix::bdiag(G1, G2)
G[lower.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]
G[upper.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]

#G[232:462, 1:231] <- vc$vcov[vc$grp == 'subject'][4]
#G[1:231, 232:462] <- vc$vcov[vc$grp == 'subject'][4]
#G[463:693, 1:231] <- vc$vcov[vc$grp == 'subject'][5]
#G[1:231, 463:693] <- vc$vcov[vc$grp == 'subject'][5]
#G[463:693, 232:462] <- vc$vcov[vc$grp == 'subject'][6]
#G[232:462, 463:693] <- vc$vcov[vc$grp == 'subject'][6]

Sigma <- Z %*% G %*% t(Z) + R 
Sigma_inv <- solve(Sigma)

P <- Sigma_inv - Sigma_inv %*% X %*% vcov(fit) %*% t(X) %*% Sigma_inv

varMargRes <- Sigma - X %*% vcov(fit) %*% t(X) 
varCondRes <- R %*% P %*% R  
varU <- G - G %*% t(Z) %*% P %*% Z %*% G

fit_bl2 <- Blackmore %>% 
  mutate(fitted = as.vector(X %*% beta),
         resm = y - fitted,
         resc = as.vector(y - fitted - Z %*% u),
         index = 1:n()) %>% 
  rowwise() %>% 
  mutate(resm_std = resm/sqrt(diag(varMargRes)[index]),
         resc_std = resc/sqrt(diag(varCondRes)[index])) %>% 
  ungroup()

unit_bl2 <- expand_grid(subjects) %>% 
  mutate(Vi = map_dbl(subjects, ~{
    ind <- Blackmore %>% 
      mutate(index = 1:n()) %>% 
      filter(subject == .x) %>% 
      pull(index)
    mi <- length(ind)
    Ei <- solve(expm::sqrtm(varMargRes[ind, ind])) %*% fit_bl$resm[ind]
    sqrt(sum((diag(mi) - Ei %*% t(Ei))^2)) / mi
  }),
  Mi = as.vector(t(u) %*% solve(varU) %*% u),
  index = 1:n())
```

```{r plot1}
ggplot(fit_bl2, aes(fitted, resm_std)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

```{r plot2}
ggplot(fit_bl2, aes(index, resm_std)) + geom_point() + geom_hline(yintercept = 0)
```

```{r plot3}
ggplot(unit_bl2, aes(index, Vi)) + geom_point()+ xlab("Unit indicies") + ylab("Modified Lesaffre-Verbeke index")
```

```{r plot4}
ggplot(fit_bl2, aes(index, resc_std)) + geom_point() + geom_hline(yintercept = 0)
```

```{r plot5}
ggplot(fit_bl2, aes(fitted, resc_std)) + geom_point() + geom_hline(yintercept = 0)
```

```{r plot6}
ggplot(fit_bl2, aes(sample = resc_std)) + 
  geom_qq() + geom_qq_line(color = "red")
```

## Simulate data for null plots based on model 2
```{r simulate}
fit.sim <- simulate(fit, nsim = 19, seed = 1234)
fit.refit <- lapply(fit.sim, refit, object = fit)
fit.simy <- lapply(fit.refit, function(x) getME(x, 'y'))
```

```{r simulate-data}
fit.sim.y <- do.call("cbind", fit.simy)
fit.sim.y <- reshape2::melt(fit.sim.y)[-1]
names(fit.sim.y) <- c(".n", "y")
fit.sim.y$.n <- as.numeric(str_extract(fit.sim.y$.n, "\\d+"))
fit.sim.y$subject <- rep(Blackmore$subject, 19)
fit.sim.y$age <- rep(Blackmore$age, 19)
fit.sim.y$group <- rep(Blackmore$group, 19)
```

```{r nulldata}
simdat <- purrr::map_dfr(1:19, function(i){
  df <- fit.sim.y %>% filter(.n == i)
  m <- lmer(y ~ age*group  + (age + I(age^2)|subject), data = df)
  
  N <- nrow(df)
  subjects <- unique(df$subject)

  y <- df$y
  X <- model.matrix(~ age*group, data = df)
  beta <- fixef(m)
  Z <- model.matrix(~ -1 + subject + subject:age + subject:I(age^2), data = df)
  u <- c(ranef(m)$subject[,1], ranef(m)$subject[,2], ranef(m)$subject[,3])
  q <- length(u)

  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == 'Residual'] * diag(N)
  G1 <- vc$vcov[vc$grp == 'subject'][1] * diag(q/3)
  G2 <- vc$vcov[vc$grp == 'subject'][2] * diag(q/3)
  G3 <- vc$vcov[vc$grp == 'subject'][3] * diag(q/3)
  G <- Matrix::bdiag(G1, G2, G3)
#G[lower.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]
#G[upper.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]

  G[232:462, 1:231] <- vc$vcov[vc$grp == 'subject'][4]
  G[1:231, 232:462] <- vc$vcov[vc$grp == 'subject'][4]
  G[463:693, 1:231] <- vc$vcov[vc$grp == 'subject'][5]
  G[1:231, 463:693] <- vc$vcov[vc$grp == 'subject'][5]
  G[463:693, 232:462] <- vc$vcov[vc$grp == 'subject'][6]
  G[232:462, 463:693] <- vc$vcov[vc$grp == 'subject'][6]

  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)

  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv

  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
```

```{r}
colnames(fit_bl)[5] <- c('y')
```

```{r lineup1, fig.height=6}
d <- lineup(true = fit_bl, samples = simdat)
ggplot(d, aes(fitted, resm_std)) + geom_point() +
  geom_hline(yintercept = 0) +
  facet_wrap( ~ .sample, ncol=5)
attr(d, "pos")
```

```{r lineup2, fig.height=6}
ggplot(d, aes(index, resm_std)) + geom_point() +
  geom_hline(yintercept = 0) +
  facet_wrap(~.sample, ncol = 5)
attr(d, "pos")
```

```{r lineup4, fig.height=6}
ggplot(d, aes(index, resc_std)) + geom_point() +
  geom_hline(yintercept = 0) +
  facet_wrap(~.sample, ncol = 5)
attr(d, "pos")
```

```{r lineup5, fig.height=6}
ggplot(d, aes(fitted, resc_std)) + geom_point() +
  geom_hline(yintercept = 0) + 
  facet_wrap(~.sample, ncol = 5)
```

```{r lineup6, fig.height=6}
ggplot(d, aes(sample = resc_std)) + 
  geom_qq() + geom_qq_line(color = "red") +
  facet_wrap(~.sample, ncol = 5)
```

```{r}
simdat_unit <- purrr::map_dfr(1:19, function(i){
  df <- fit.sim.y %>% filter(.n == i)
  m <- lmer(y ~ age*group  + (age + I(age^2)|subject), data = df)
  
  N <- nrow(df)
  subjects <- unique(df$subject)

  y <- df$y
  X <- model.matrix(~ age*group, data = df)
  beta <- fixef(m)
  Z <- model.matrix(~ -1 + subject + subject:age + subject:I(age^2), data = df)
  u <- c(ranef(m)$subject[,1], ranef(m)$subject[,2], ranef(m)$subject[,3])
  q <- length(u)

  vc <- as.data.frame(VarCorr(m))
  R <- vc$vcov[vc$grp == 'Residual'] * diag(N)
  G1 <- vc$vcov[vc$grp == 'subject'][1] * diag(q/3)
  G2 <- vc$vcov[vc$grp == 'subject'][2] * diag(q/3)
  G3 <- vc$vcov[vc$grp == 'subject'][3] * diag(q/3)
  G <- Matrix::bdiag(G1, G2, G3)
#G[lower.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]
#G[upper.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]

  G[232:462, 1:231] <- vc$vcov[vc$grp == 'subject'][4]
  G[1:231, 232:462] <- vc$vcov[vc$grp == 'subject'][4]
  G[463:693, 1:231] <- vc$vcov[vc$grp == 'subject'][5]
  G[1:231, 463:693] <- vc$vcov[vc$grp == 'subject'][5]
  G[463:693, 232:462] <- vc$vcov[vc$grp == 'subject'][6]
  G[232:462, 463:693] <- vc$vcov[vc$grp == 'subject'][6]

  Sigma <- Z %*% G %*% t(Z) + R 
  Sigma_inv <- solve(Sigma)

  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv

  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  expand_grid(subjects) %>% 
    mutate(Vi = map_dbl(subjects, ~{
      ind <- df %>% 
        mutate(index = 1:n()) %>% 
        filter(subject == .x) %>% 
        pull(index)
      mi <- length(ind)
      Ei <- solve(expm::sqrtm(varMargRes[ind, ind])) %*% resm[ind]
      sqrt(sum((diag(mi) - Ei %*% t(Ei))^2)) / mi
      }),
      Mi = as.vector(t(u) %*% solve(varU) %*% u),
      index = 1:n(),
      .n = i)
})
```

```{r lineup3, fig.height = 6}
d2 <- lineup(true = unit_bl, samples = simdat_unit)
ggplot(d2, aes(index, Vi)) + geom_point()+
  facet_wrap(~.sample, ncol = 5)
attr(d2, "pos")
```

```{r lineup7, fig.height=6}
ggplot(d2, aes(index, Mi)) + geom_point() + facet_wrap(~.sample, ncol = 5)
```

```{r lineup8, fig.height=6}
ggplot(d2, aes(sample = Mi)) + 
  geom_qq(distribution = stats::qchisq,
          dparams = list(df = q)) +
  geom_qq_line(color = "red",
               distribution = stats::qchisq,
               dparams = list(df = q)) +
  facet_wrap(~.sample, ncol = 5)
```

## Model 4 with slight noise

```{r}
N <- nrow(Blackmore)
subjects <- unique(Blackmore$subject)

y <- Blackmore$log.exercise
X <- model.matrix(~ age*group, data = Blackmore)
beta <- fixef(fit)
Z <- model.matrix(~ -1 + subject + subject:age + subject:I(age^2), data = Blackmore)
u <- c(ranef(fit)$subject[,1], ranef(fit)$subject[,2], ranef(fit)$subject[,3])
q <- length(u)

vc <- as.data.frame(VarCorr(fit))
R <- vc$vcov[vc$grp == 'Residual'] * diag(N)
G1 <- vc$vcov[vc$grp == 'subject'][1] * diag(q/3)
G2 <- vc$vcov[vc$grp == 'subject'][2] * diag(q/3)
G3 <- vc$vcov[vc$grp == 'subject'][3] * diag(q/3)
G <- Matrix::bdiag(G1, G2, G3)
#G[lower.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]
#G[upper.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]

G[232:462, 1:231] <- vc$vcov[vc$grp == 'subject'][4]
G[1:231, 232:462] <- vc$vcov[vc$grp == 'subject'][4]
G[463:693, 1:231] <- vc$vcov[vc$grp == 'subject'][5]
G[1:231, 463:693] <- vc$vcov[vc$grp == 'subject'][5]
G[463:693, 232:462] <- vc$vcov[vc$grp == 'subject'][6]
G[232:462, 463:693] <- vc$vcov[vc$grp == 'subject'][6]

y <- as.vector(mvtnorm::rmvnorm(1, mean = X %*% beta, sigma = Z %*% G %*% t(Z) + rnorm(N, mean =0, sd = 2), checkSymmetry = FALSE))

newdat1 <- tibble(Blackmore, y)
head(newdat1)

fit4 <- lmer(y ~ age*group  + (age + I(age^2)|subject), data = newdat1)

summary(fit4)
```

```{r}
N <- nrow(newdat1)
subjects <- unique(newdat1$subject)

y <- newdat1$y
X <- model.matrix(~ age*group, data = newdat1)
beta <- fixef(fit4)
Z <- model.matrix(~ -1 + subject + subject:age + subject:I(age^2), data = newdat1)
u <- c(ranef(fit4)$subject[,1], ranef(fit4)$subject[,2], ranef(fit4)$subject[,3])
q <- length(u)

vc <- as.data.frame(VarCorr(fit4))
R <- vc$vcov[vc$grp == 'Residual'] * diag(N)
G1 <- vc$vcov[vc$grp == 'subject'][1] * diag(q/3)
G2 <- vc$vcov[vc$grp == 'subject'][2] * diag(q/3)
G3 <- vc$vcov[vc$grp == 'subject'][3] * diag(q/3)
G <- Matrix::bdiag(G1, G2, G3)
#G[lower.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]
#G[upper.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]

G[232:462, 1:231] <- vc$vcov[vc$grp == 'subject'][4]
G[1:231, 232:462] <- vc$vcov[vc$grp == 'subject'][4]
G[463:693, 1:231] <- vc$vcov[vc$grp == 'subject'][5]
G[1:231, 463:693] <- vc$vcov[vc$grp == 'subject'][5]
G[463:693, 232:462] <- vc$vcov[vc$grp == 'subject'][6]
G[232:462, 463:693] <- vc$vcov[vc$grp == 'subject'][6]

Sigma <- Z %*% G %*% t(Z) + R 
Sigma_inv <- solve(Sigma)

P <- Sigma_inv - Sigma_inv %*% X %*% vcov(fit4) %*% t(X) %*% Sigma_inv

varMargRes <- Sigma - X %*% vcov(fit4) %*% t(X) 
varCondRes <- R %*% P %*% R  
varU <- G - G %*% t(Z) %*% P %*% Z %*% G

fit_b4 <- newdat1 %>% 
  mutate(fitted = as.vector(X %*% beta),
         resm = y - fitted,
         resc = as.vector(y - fitted - Z %*% u),
         index = 1:n()) %>% 
  rowwise() %>% 
  mutate(resm_std = resm/sqrt(diag(varMargRes)[index]),
         resc_std = resc/sqrt(diag(varCondRes)[index])) %>% 
  ungroup()

unit_b4 <- expand_grid(subjects) %>% 
  mutate(Vi = map_dbl(subjects, ~{
    ind <- newdat1 %>% 
      mutate(index = 1:n()) %>% 
      filter(subject %in%  .x) %>% 
      pull(index)
    mi <- length(ind)
    Ei <- solve(expm::sqrtm(varMargRes[ind, ind])) %*% fit_b4$resm[ind]
    sqrt(sum((diag(mi) - Ei %*% t(Ei))^2)) / mi
  }),
  Mi = as.vector(t(u) %*% solve(varU) %*% u),
  index = 1:n())
```

```{r m4-plot1}
ggplot(fit_b4, aes(fitted, resm_std)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

```{r m4-plot2}
ggplot(fit_b4, aes(index, resm_std)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

```{r m4-plot3}
ggplot(unit_b4, aes(index, Vi)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

```{r m4-plot4}
ggplot(fit_b4, aes(index, resc_std)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

```{r m4-plot5}
ggplot(fit_b4, aes(fitted, resc_std)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

```{r m4-plot6}
ggplot(fit_b4, aes(sample = resc_std)) + 
  geom_qq() + geom_qq_line(color = "red")
```

```{r m4-plot7}
ggplot(unit_b4, aes(index, Mi)) + geom_point() + xlab("Unit index") + ylab("Manhalanobis distance")
```

```{r m4-plot8}
ggplot(unit_b4, aes(sample = Mi)) + 
  geom_qq(distribution = stats::qchisq,
          dparams = list(df = q)) +
  geom_qq_line(color = "red",
               distribution = stats::qchisq,
               dparams = list(df = q))
```

## Model 5 with extreme value

```{r}
N <- nrow(Blackmore)
subjects <- unique(Blackmore$subject)

y <- Blackmore$log.exercise
X <- model.matrix(~ age*group, data = Blackmore)
beta <- fixef(fit)
Z <- model.matrix(~ -1 + subject + subject:age + subject:I(age^2), data = Blackmore)
u <- c(ranef(fit)$subject[,1], ranef(fit)$subject[,2], ranef(fit)$subject[,3])
q <- length(u)

vc <- as.data.frame(VarCorr(fit))
R <- vc$vcov[vc$grp == 'Residual'] * diag(N)
G1 <- vc$vcov[vc$grp == 'subject'][1] * diag(q/3)
G2 <- vc$vcov[vc$grp == 'subject'][2] * diag(q/3)
G3 <- vc$vcov[vc$grp == 'subject'][3] * diag(q/3)
G <- Matrix::bdiag(G1, G2, G3)
#G[lower.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]
#G[upper.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]

G[232:462, 1:231] <- vc$vcov[vc$grp == 'subject'][4]
G[1:231, 232:462] <- vc$vcov[vc$grp == 'subject'][4]
G[463:693, 1:231] <- vc$vcov[vc$grp == 'subject'][5]
G[1:231, 463:693] <- vc$vcov[vc$grp == 'subject'][5]
G[463:693, 232:462] <- vc$vcov[vc$grp == 'subject'][6]
G[232:462, 463:693] <- vc$vcov[vc$grp == 'subject'][6]

ny <- as.vector(mvtnorm::rmvnorm(1, mean = X %*% beta, sigma = Z %*% G %*% t(Z) + rnorm(N, mean =0, sd = 10), checkSymmetry = FALSE))

newdat2 <- tibble(Blackmore, ny)
head(newdat2)
```
```{r}
fit5 <- lmer(y ~ age*group  + (age + I(age^2)|subject), data = newdat2)

summary(fit5)
```
```{r}
N <- nrow(newdat2)
subjects <- unique(newdat2$subject)

y <- newdat2$ny
X <- model.matrix(~ age*group, data = newdat2)
beta <- fixef(fit5)
Z <- model.matrix(~ -1 + subject + subject:age + subject:I(age^2), data = newdat2)
u <- c(ranef(fit5)$subject[,1], ranef(fit5)$subject[,2], ranef(fit5)$subject[,3])
q <- length(u)

vc <- as.data.frame(VarCorr(fit5))
R <- vc$vcov[vc$grp == 'Residual'] * diag(N)
G1 <- vc$vcov[vc$grp == 'subject'][1] * diag(q/3)
G2 <- vc$vcov[vc$grp == 'subject'][2] * diag(q/3)
G3 <- vc$vcov[vc$grp == 'subject'][3] * diag(q/3)
G <- Matrix::bdiag(G1, G2, G3)
#G[lower.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]
#G[upper.tri(G)] <- vc$vcov[vc$grp == 'subject'][3]

G[232:462, 1:231] <- vc$vcov[vc$grp == 'subject'][4]
G[1:231, 232:462] <- vc$vcov[vc$grp == 'subject'][4]
G[463:693, 1:231] <- vc$vcov[vc$grp == 'subject'][5]
G[1:231, 463:693] <- vc$vcov[vc$grp == 'subject'][5]
G[463:693, 232:462] <- vc$vcov[vc$grp == 'subject'][6]
G[232:462, 463:693] <- vc$vcov[vc$grp == 'subject'][6]

Sigma <- Z %*% G %*% t(Z) + R 
Sigma_inv <- solve(Sigma)

P <- Sigma_inv - Sigma_inv %*% X %*% vcov(fit5) %*% t(X) %*% Sigma_inv

varMargRes <- Sigma - X %*% vcov(fit5) %*% t(X) 
varCondRes <- R %*% P %*% R  
varU <- G - G %*% t(Z) %*% P %*% Z %*% G

fit_b5 <- newdat2 %>% 
  mutate(fitted = as.vector(X %*% beta),
         resm = y - fitted,
         resc = as.vector(y - fitted - Z %*% u),
         index = 1:n()) %>% 
  rowwise() %>% 
  mutate(resm_std = resm/sqrt(diag(varMargRes)[index]),
         resc_std = resc/sqrt(diag(varCondRes)[index])) %>% 
  ungroup()

unit_b5 <- expand_grid(subjects) %>% 
  mutate(Vi = map_dbl(subjects, ~{
    ind <- newdat2 %>% 
      mutate(index = 1:n()) %>% 
      filter(subject %in%  .x) %>% 
      pull(index)
    mi <- length(ind)
    Ei <- solve(expm::sqrtm(varMargRes[ind, ind])) %*% fit_b5$resm[ind]
    sqrt(sum((diag(mi) - Ei %*% t(Ei))^2)) / mi
  }),
  Mi = as.vector(t(u) %*% solve(varU) %*% u),
  index = 1:n())
```

```{r m5-plot1}
ggplot(fit_b5, aes(fitted, resm_std)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

```{r m5-plot2}
ggplot(fit_b5, aes(index, resm_std)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

```{r m5-plot3}
ggplot(unit_b5, aes(index, Vi)) + geom_point()+ xlab("Unit indicies") + ylab("Modified Lesaffre-Verbeke index")
```

```{r m5-plot4}
ggplot(fit_b5, aes(index, resc_std)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

```{r m5-plot5}
ggplot(fit_b5, aes(fitted, resc_std)) +
  geom_hline(yintercept = 0) +
  geom_point()
```

```{r m5-plot6}
ggplot(fit_b5, aes(sample = resc_std)) + 
  geom_qq() + geom_qq_line(color = "red")
```

```{r m5-plot7}
ggplot(unit_b5, aes(index, Mi)) + geom_point() + xlab("Unit index") + ylab("Manhalanobis distance")
```

```{r m5-plot8}
ggplot(unit_b5, aes(sample = Mi)) + 
  geom_qq(distribution = stats::qchisq,
          dparams = list(df = q)) +
  geom_qq_line(color = "red",
               distribution = stats::qchisq,
               dparams = list(df = q))
```