---
title: "case6 noise test"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(HLMdiag)
library(lme4)
library(nlme)
library(ggplot2)
library(nullabor)
library(ggforce)
library(dplyr)
library(stringr)
library(mvtnorm)
library(MASS)
library(patchwork)
```

Autism data has 155 children between the ages of 2 and 13 who were diagnosed with either autism spectrum disorder or non-spectrum developmental delays at age 2.

It contains 604 observations with 7 variables:

- `childid`: Child ID
- `sicdegp`: Sequenced Inventory of Communication Development group (an assessment of expressive language development) with levels low, mod, and high  ## language used 
- `age2`: Age (in years) centered arond age 2 (age at diagnosis)
- `vsae`: Vineland Socialization Age Equivalent ## social skill
- `gender`: Child's gender, female and male
- `race`: Child's race, white and non-white
- `bestest2`: Diagnosis at age 2, autism and pdd

```{r}
data(autism)
str(autism)
summary(autism)
length(unique(autism$childid))


```

- subject-level variables:
+ `chilidid`
+ `sicdegp`
+ `gender`
+ `race`
+ `bestest2`

```{r}
agen <- ggplot(autism, aes(age2, log10(vsae))) +
  geom_point() +
  facet_wrap_paginate(~childid, nrow = 5, ncol = 5, page = 1) +
  geom_smooth(method = "lm", se = F)+
  ggtitle("No noise")
```

- `age2` has the relative positive relationship with `vsae` except childid 18
- It seems to have the similar intercept but with different slopes.

```{r}
genn <- ggplot(autism, aes(gender, vsae)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("No noise")
```

there is no much difference between male and female with respective to `vsae`.

```{r}
racegenn <- ggplot(autism, aes(interaction(gender, race), vsae)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("No noise")
```

```{r}
sicn <- ggplot(autism, aes(sicdegp, vsae, fill = race)) +
  geom_boxplot() +
  scale_y_log10()
bestn <- ggplot(autism, aes(bestest2, vsae)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("No noise")
```

At this stage, the variables, interaction of `gender` and `race`, `sicdegp`, `age2` and `bestest2` include in the model as matrix of fixed effect. 

From the `age2` versus `vsae` plot, the intercept seems to be same while the slope is different for each different children. Then we treat the random effect with random slope. As Adam mentioned, the model for LMM needs the quadratic random slope.

```{r model}
colnames(autism)[4] <- c("y")


```


## Noise 

- we add 20% of the total median response values to roughly 20% of
observations at random.

```{r}

median_noise <- function(noise){

set.seed(2639)
ind <- sample(604, 120, replace = F)
autism_repc3 <- autism
autism_repc3[ind, ]$y <- autism_repc3[ind, ]$y + median(autism_repc3$y) * noise

return (autism_repc3)
}


```

```{r fittedfn}
autism_extract_fitted_mod <- function(mod, data) {
 
 
  # n <- getME(mod, "n")
   N <- nrow(data)


  y <- getME(mod, "y")
  X <- getME(mod, "X")
  beta <- getME(mod, "beta")
  Z <- getME(mod, "Z")
  u <- getME(mod, "b")
  q <- getME(mod, "q")

  nrfacs <- getME(mod,"n_rfacs")
  num <- 0

    if(nrfacs>1)
    {
 a <-  data %>%
  select_if((names(data) %in% names(random.effects(mod)))) 
 
 for(i in 1:nrfacs)
 {
  num[i] <- nrow(unique(a[i]))
 }
  vc <- as.data.frame(VarCorr(mod))
  
   R <- vc$vcov[3] * diag(N) # covariance matrix of random errors
  G1 <- vc$vcov[1] * diag(num[2])
  G2 <- vc$vcov[2] * diag(num[1])

  G <- Matrix::bdiag(G1, G2)
    } else   
  {
  num <- data %>%
  select_if((names(data) %in% names(random.effects(mod)))) %>%
  unique() %>%
  nrow()

  vc <- as.data.frame(VarCorr(mod))
   R <-  vc$vcov[3] * diag(N)
  G1 <- vc$vcov[1] * diag(num)
  G2 <- vc$vcov[2] * diag(num)
  G <- Matrix::bdiag(G1, G2)
}


 Sigma <- Z %*% G %*% t(Z) + R
  Sigma_inv <- solve(Sigma)

  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(mod) %*% t(X) %*% Sigma_inv

  varMargRes <- Sigma - X %*% vcov(mod) %*% t(X)
  varCondRes <- R %*% P %*% R
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G

  fitted_df <- data %>%
    dplyr::mutate(
      fitted = as.vector(X %*% beta),
      resm = y - fitted,
      resc = as.vector(y - fitted - Z %*% u),
      index = 1:n()
    ) %>%
    mutate(
      resm_std = resm / sqrt(diag(varMargRes)[index]),
      resc_std = resc / sqrt(diag(varCondRes)[index])
    ) %>%
    ungroup()
}
```

```{r lcrfn}
autism_extract_lcr_mod <- function(mod, data) {
  

  
  N <- nrow(data)
 y <- getME(mod, "y")
  X <- getME(mod, "X")
  beta <- getME(mod, "beta")
  Z <- getME(mod, "Z")
  u <- getME(mod, "b")
  q <- getME(mod, "q")
  
  nrfacs <- getME(mod,"n_rfacs")
  num <- 0

    if(nrfacs>1)
    {
 a <-  data %>%
  select_if((names(data) %in% names(random.effects(mod)))) 
 
 for(i in 1:nrfacs)
 {
  num[i] <- nrow(unique(a[i]))
 }
  vc <- as.data.frame(VarCorr(mod))
  
   R <- vc$vcov[3] * diag(N) # covariance matrix of random errors
  G1 <- vc$vcov[1] * diag(num[2])
  G2 <- vc$vcov[2] * diag(num[1])

  G <- Matrix::bdiag(G1, G2)
    } else   
  {
  num <- data %>%
  select_if((names(data) %in% names(random.effects(mod)))) %>%
  unique() %>%
  nrow()

  vc <- as.data.frame(VarCorr(mod))
   R <-  vc$vcov[3] * diag(N)
  G1 <- vc$vcov[1] * diag(num)
  G2 <- vc$vcov[2] * diag(num)
  G <- Matrix::bdiag(G1, G2)
}

  Sigma <- Z %*% G %*% t(Z) + R

  Sigma_inv <- solve(Sigma)

  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(mod) %*% t(X) %*% Sigma_inv

  varMargRes <- Sigma - X %*% vcov(mod) %*% t(X)
  varCondRes <- R %*% P %*% R
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G

  fitted <- as.vector(X %*% beta)
  resm <- y - fitted
  resc <- as.vector(y - fitted - Z %*% u)
  index <- 1:nrow(data)
  resm_std <- resm / sqrt(diag(varMargRes)[index])
  resc_std <- resc / sqrt(diag(varCondRes)[index])

  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half), symmetric = T, only.values = FALSE)

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(N-p)])))) %*% t(auxqn$vectors[1:N,1:(N-p)]) %*% solve(expm::sqrtm(R[1:N,1:N]))

  var.resmcp <- lt %*% varCondRes[1:N, 1:N] %*% t(lt)

  resmcp <- (lt %*% resc[1:N]) / sqrt(diag(var.resmcp))

  resmcp_sl <- tibble::tibble(resmcp)

  return(resmcp_sl)
}
```

```{r simulatefn}
autism_sim <- function(mod, data, nsim = 19, seed, std = FALSE) {
  fit_sim <- simulate(mod, nsim = nsim, seed = seed, std = std)
  fit_refit <- lapply(fit_sim, refit, object = mod)
  fit_simy <- lapply(fit_refit, function(x) getME(x, "y"))
  fit_simy_y <- do.call("cbind", fit_simy)
  fit_simy_y <- reshape2::melt(fit_simy_y)[-1]
  names(fit_simy_y) <- c(".n", "y")
  fit_simy_y$.n <- as.numeric(str_extract(fit_simy_y$.n, "\\d+"))
  fit_simy_y$age2 <- rep(data$age2, 19)
  fit_simy_y$sicdegp <- rep(data$sicdegp, 19)
  fit_simy_y$gender <- rep(data$gender, 19)
  fit_simy_y$race <- rep(data$race, 19)
  fit_simy_y$bestest2 <- rep(data$bestest2, 19)
  fit_simy_y$childid <- rep(data$childid, 19)
  return(fit_simy_y)
}
```


```{r}
std_res <- function(data) {
  purrr::map_dfr(1:19, function(i) {
  df <- data %>% filter(.n == i)
  m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = df)
  
  N <- nrow(df)
  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")

 nrfacs <- getME(m,"n_rfacs")
  num <- 0

    if(nrfacs>1)
    {
 a <-  data %>%
  select_if((names(data) %in% names(random.effects(m)))) 
 
 for(i in 1:nrfacs)
 {
  num[i] <- nrow(unique(a[i]))
 }
  vc <- as.data.frame(VarCorr(m))
  
   R <- vc$vcov[3] * diag(N) # covariance matrix of random errors
  G1 <- vc$vcov[1] * diag(num[2])
  G2 <- vc$vcov[2] * diag(num[1])

  G <- Matrix::bdiag(G1, G2)
    } else   
  {
  num <- data %>%
  select_if((names(data) %in% names(random.effects(m)))) %>%
  unique() %>%
  nrow()

  vc <- as.data.frame(VarCorr(m))
   R <-  vc$vcov[3] * diag(N)
  G1 <- vc$vcov[1] * diag(num)
  G2 <- vc$vcov[2] * diag(num)
  G <- Matrix::bdiag(G1, G2)
}


  Sigma <- Z %*% G %*% t(Z) + R 

  Sigma_inv <- solve(Sigma)


  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv

  varMargRes <- Sigma - X %*% vcov(m) %*% t(X) 
  varCondRes <- R %*% P %*% R  
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G
  
  fitted = as.vector(X %*% beta)
  resm = y - fitted
  resc = y - fitted - as.vector(Z %*% u)
  index = 1:nrow(df)
  resm_std = resm / sqrt(diag(varMargRes)[index])
  resc_std = resc / sqrt(diag(varCondRes)[index])
  
  tibble::tibble(df, fitted, resm_std, resc_std, index)
})
}
```


```{r}
lcr_res <- function(data) {
  
  purrr::map_dfr(1:19, function(i) {
  df <- data %>% filter(.n == i)
 m <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = df)

  N <- nrow(df)
  num <- data %>%
  select_if((names(data) %in% names(random.effects(m)))) %>%
  unique() %>%
  nrow()

  y <- getME(m, "y")
  X <- getME(m, "X")
  beta <- getME(m, "beta")
  Z <- getME(m, "Z")
  u <- getME(m, "b")
  q <- getME(m, "q")

 nrfacs <- getME(m,"n_rfacs")
 num <- 0 

  if(nrfacs>1)
    {
 a <-  data %>%
  select_if((names(data) %in% names(random.effects(m)))) 
 
 for(i in 1:nrfacs)
 {
  num[i] <- nrow(unique(a[i]))
 }
  vc <- as.data.frame(VarCorr(m))
  
   R <- vc$vcov[3] * diag(N) # covariance matrix of random errors
  G1 <- vc$vcov[1] * diag(num[2])
  G2 <- vc$vcov[2] * diag(num[1])

  G <- Matrix::bdiag(G1, G2)
    } else   
  {
  num <- data %>%
  select_if((names(data) %in% names(random.effects(m)))) %>%
  unique() %>%
  nrow()

  vc <- as.data.frame(VarCorr(m))
   R <-  vc$vcov[3] * diag(N)
  G1 <- vc$vcov[1] * diag(num)
  G2 <- vc$vcov[2] * diag(num)
  G <- Matrix::bdiag(G1, G2)
}

  Sigma <- Z %*% G %*% t(Z) + R
  Sigma_inv <- solve(Sigma)

  P <- Sigma_inv - Sigma_inv %*% X %*% vcov(m) %*% t(X) %*% Sigma_inv

  varMargRes <- Sigma - X %*% vcov(m) %*% t(X)
  varCondRes <- R %*% P %*% R
  varU <- G - G %*% t(Z) %*% P %*% Z %*% G

  fitted <- as.vector(X %*% beta)
  resm <- y - fitted
  resc <- y - fitted - as.vector(Z %*% u)
  index <- 1:nrow(df)
  resm_std <- resm / sqrt(diag(varMargRes)[index])
  resc_std <- resc / sqrt(diag(varCondRes)[index])

  R_half <- expm::sqrtm(R)

  auxqn <- eigen((R_half %*% P %*% R_half),
    symmetric = T,
    only.values = FALSE
  )

  p <- length(beta)

  lt <- sqrt(solve(diag((auxqn$values[1:(N - p)])))) %*% t(auxqn$vectors[1:N, 1:(N - p)]) %*% solve(expm::sqrtm(R[1:N, 1:N]))

  var_resmcp <- lt %*% varCondRes[1:N, 1:N] %*% t(lt)

  resmcp <- (lt %*% resc[1:N]) / sqrt(diag(var_resmcp))
  .n <- i

  tibble::tibble(.n, resmcp)
})
  
}
```

```{r}
obs_noise <- function(noise){

set.seed(2639)
ind <- sample(604,noise*(nrow(autism)), replace = F)
autism_repc3 <- autism
autism_repc3[ind, ]$y <- autism_repc3[ind, ]$y + median(autism_repc3$y) * 0.2

return (autism_repc3)
}



```

```{r}
autism_mod <- lmer(y ~ age2 + sicdegp + gender:race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = autism)
autism_fitted <- autism_extract_fitted_mod(autism_mod, autism)
autism_lcr <- autism_extract_lcr_mod(autism_mod, autism)
```

# Data plots

```{r}
 a0 <- ggplot(autism_s1_fitted, aes(index, resm_std, color = gender, shape = race)) +
  geom_point()

 b0 <- ggplot(autism_s1_fitted, aes(interaction(gender, race), resc_std)) +
  geom_boxplot() +
  ylab("Standardised conditional residuals") +
  theme()

c0 <- ggplot(autism_s1_fitted, aes(sample = resc_std)) +
  geom_qq() +
  geom_qq_line(color = "red")

d0 <- ggplot(autism_s1_lcr, aes(sample = resmcp)) +
  geom_qq() +
  geom_qq_line(color = "red")
```


### set 1

```{r}
autism_set1 <- median_noise(0.2)

age1 <- ggplot(autism_set1, aes(age2, log10(y))) +
  geom_point() +
  facet_wrap_paginate(~childid, nrow = 5, ncol = 5, page = 1) +
  geom_smooth(method = "lm", se = F)+
  ggtitle("20%")

gender1 <- ggplot(autism_set1, aes(gender, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("20%")

racegen1 <- ggplot(autism_set1, aes(interaction(gender, race), y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("20%")

sic1 <- ggplot(autism_set1, aes(sicdegp, y, fill = race)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("20%")

best1 <- ggplot(autism_set1, aes(bestest2, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("20%")


```


```{r}
autism_s1_mod <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = autism_set1)
autism_s1_fitted <- autism_extract_fitted_mod(autism_s1_mod, autism_set1)
autism_s1_lcr <- autism_extract_lcr_mod(autism_s1_mod, autism_set1)
```

# Data plots

```{r}
 a1 <- ggplot(autism_s1_fitted, aes(index, resm_std, color = gender, shape = race)) +
  geom_point()

 b1 <- ggplot(autism_s1_fitted, aes(interaction(gender, race), resc_std)) +
  geom_boxplot() +
  ylab("Standardised conditional residuals") +
  theme()

c1 <- ggplot(autism_s1_fitted, aes(sample = resc_std)) +
  geom_qq() +
  geom_qq_line(color = "red")

d1 <- ggplot(autism_s1_lcr, aes(sample = resmcp)) +
  geom_qq() +
  geom_qq_line(color = "red")
```

## set 2

```{r}

autism_set2 <- median_noise(0.25)

age2 <- ggplot(autism_set2, aes(age2, log10(y))) +
  geom_point() +
  facet_wrap_paginate(~childid, nrow = 5, ncol = 5, page = 1) +
  geom_smooth(method = "lm", se = F)+
  ggtitle("25%")

gender2 <- ggplot(autism_set2, aes(gender, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("25%")

racegen2 <- ggplot(autism_set2, aes(interaction(gender, race), y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("25%")

sic2 <- ggplot(autism_set2, aes(sicdegp, y, fill = race)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("25%")

best2 <- ggplot(autism_set2, aes(bestest2, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("25%")



```

```{r}
autism_s2_mod <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = autism_set2)
autism_s2_fitted <- autism_extract_fitted_mod(autism_s2_mod, autism_set2)
autism_s2_lcr <- autism_extract_lcr_mod(autism_s2_mod, autism_set2)
```

# Data plots

```{r}
a2 <- ggplot(autism_s2_fitted, aes(index, resm_std, color = gender, shape = race)) +
  geom_point()

 b2<- ggplot(autism_s2_fitted, aes(interaction(gender, race), resc_std)) +
  geom_boxplot() +
  ylab("Standardised conditional residuals") +
  theme()


c2 <- ggplot(autism_s2_fitted, aes(sample = resc_std)) +
  geom_qq() +
  geom_qq_line(color = "red")

d2 <- ggplot(autism_s2_lcr, aes(sample = resmcp)) +
  geom_qq() +
  geom_qq_line(color = "red")


```


## set 3



```{r}

autism_set3 <- median_noise(0.3)

age3 <- ggplot(autism_set3, aes(age2, log10(y))) +
  geom_point() +
  facet_wrap_paginate(~childid, nrow = 5, ncol = 5, page = 1) +
  geom_smooth(method = "lm", se = F)+
  ggtitle("30%")

gender3 <- ggplot(autism_set3, aes(gender, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("30%")

racegen3 <- ggplot(autism_set3, aes(interaction(gender, race), y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("30%")

sic3 <- ggplot(autism_set3, aes(sicdegp, y, fill = race)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("30%")

best3 <- ggplot(autism_set3, aes(bestest2, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("30%")



```

```{r}
autism_s3_mod <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = autism_set3)
autism_s3_fitted <- autism_extract_fitted_mod(autism_s3_mod, autism_set3)
autism_s3_lcr <- autism_extract_lcr_mod(autism_s3_mod, autism_set3)
```

# Data plots

```{r}
a3 <- ggplot(autism_s3_fitted, aes(index, resm_std, color = gender, shape = race)) +
  geom_point()

 b3<- ggplot(autism_s3_fitted, aes(interaction(gender, race), resc_std)) +
  geom_boxplot() +
  ylab("Standardised conditional residuals") +
  theme()


c3 <- ggplot(autism_s3_fitted, aes(sample = resc_std)) +
  geom_qq() +
  geom_qq_line(color = "red")

d3 <- ggplot(autism_s3_lcr, aes(sample = resmcp)) +
  geom_qq() +
  geom_qq_line(color = "red")

```

# set 4


```{r}

autism_set4 <- median_noise(0.35)

age4 <- ggplot(autism_set4, aes(age2, log10(y))) +
  geom_point() +
  facet_wrap_paginate(~childid, nrow = 5, ncol = 5, page = 1) +
  geom_smooth(method = "lm", se = F)+
  ggtitle("35%")

gender4 <- ggplot(autism_set4, aes(gender, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("35%")

racegen4 <- ggplot(autism_set4, aes(interaction(gender, race), y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("35%")

sic4 <- ggplot(autism_set4, aes(sicdegp, y, fill = race)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("35%")

best4 <- ggplot(autism_set4, aes(bestest2, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("35%")



```

```{r}
autism_s4_mod <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = autism_set4)
autism_s4_fitted <- autism_extract_fitted_mod(autism_s4_mod, autism_set4)
autism_s4_lcr <- autism_extract_lcr_mod(autism_s4_mod, autism_set4)
```

# Data plots

```{r}
a4 <- ggplot(autism_s4_fitted, aes(index, resm_std, color = gender, shape = race)) +
  geom_point()

b4<- ggplot(autism_s4_fitted, aes(interaction(gender, race), resc_std)) +
  geom_boxplot() +
  ylab("Standardised conditional residuals") +
  theme()


c4 <- ggplot(autism_s4_fitted, aes(sample = resc_std)) +
  geom_qq() +
  geom_qq_line(color = "red")

d4 <- ggplot(autism_s4_lcr, aes(sample = resmcp)) +
  geom_qq() +
  geom_qq_line(color = "red")


```

### set 5 : Percentage of observations changed

```{r}
autism_set5 <- obs_noise(0.25)

age5 <- ggplot(autism_set5, aes(age2, log10(y))) +
  geom_point() +
  facet_wrap_paginate(~childid, nrow = 5, ncol = 5, page = 1) +
  geom_smooth(method = "lm", se = F)+
  ggtitle("20%")

gender5 <- ggplot(autism_set5, aes(gender, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("20%")

racegen5 <- ggplot(autism_set5, aes(interaction(gender, race), y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("20%")

sic5 <- ggplot(autism_set5, aes(sicdegp, y, fill = race)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("20%")

best5 <- ggplot(autism_set5, aes(bestest2, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("20%")


```


```{r}
autism_s5_mod <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = autism_set5)
autism_s5_fitted <- autism_extract_fitted_mod(autism_s5_mod, autism_set5)
autism_s5_lcr <- autism_extract_lcr_mod(autism_s5_mod, autism_set5)
```

# Data plots

```{r}
 a5 <- ggplot(autism_s5_fitted, aes(index, resm_std, color = gender, shape = race)) +
  geom_point()

 b5 <- ggplot(autism_s5_fitted, aes(interaction(gender, race), resc_std)) +
  geom_boxplot() +
  ylab("Standardised conditional residuals") +
  theme()

c5 <- ggplot(autism_s5_fitted, aes(sample = resc_std)) +
  geom_qq() +
  geom_qq_line(color = "red")

d5 <- ggplot(autism_s5_lcr, aes(sample = resmcp)) +
  geom_qq() +
  geom_qq_line(color = "red")
```

## set 6

```{r}

autism_set6 <- median_noise(0.3)

age6 <- ggplot(autism_set6, aes(age2, log10(y))) +
  geom_point() +
  facet_wrap_paginate(~childid, nrow = 5, ncol = 5, page = 1) +
  geom_smooth(method = "lm", se = F)+
  ggtitle("30%")

gender6 <- ggplot(autism_set6, aes(gender, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("30%")

racegen6 <- ggplot(autism_set6, aes(interaction(gender, race), y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("30%")

sic6 <- ggplot(autism_set6, aes(sicdegp, y, fill = race)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("30%")

best6 <- ggplot(autism_set6, aes(bestest2, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("30%")



```

```{r}
autism_s6_mod <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = autism_set6)
autism_s6_fitted <- autism_extract_fitted_mod(autism_s6_mod, autism_set6)
autism_s6_lcr <- autism_extract_lcr_mod(autism_s6_mod, autism_set6)
```

# Data plots

```{r}
a6 <- ggplot(autism_s6_fitted, aes(index, resm_std, color = gender, shape = race)) +
  geom_point()

 b6<- ggplot(autism_s6_fitted, aes(interaction(gender, race), resc_std)) +
  geom_boxplot() +
  ylab("Standardised conditional residuals") +
  theme()


c6 <- ggplot(autism_s6_fitted, aes(sample = resc_std)) +
  geom_qq() +
  geom_qq_line(color = "red")

d6<- ggplot(autism_s6_lcr, aes(sample = resmcp)) +
  geom_qq() +
  geom_qq_line(color = "red")


```


## set 3



```{r}

autism_set7 <- median_noise(0.35)

age7 <- ggplot(autism_set7, aes(age2, log10(y))) +
  geom_point() +
  facet_wrap_paginate(~childid, nrow = 5, ncol = 5, page = 1) +
  geom_smooth(method = "lm", se = F)+
  ggtitle("35%")

gender7 <- ggplot(autism_set7, aes(gender, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("35%")

racegen7 <- ggplot(autism_set7, aes(interaction(gender, race), y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("35%")

sic7<- ggplot(autism_set7, aes(sicdegp, y, fill = race)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("35%")

best7 <- ggplot(autism_set7, aes(bestest2, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("35%")



```

```{r}
autism_s7_mod <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = autism_set7)
autism_s7_fitted <- autism_extract_fitted_mod(autism_s7_mod, autism_set7)
autism_s7_lcr <- autism_extract_lcr_mod(autism_s7_mod, autism_set7)
```

# Data plots

```{r}
a7 <- ggplot(autism_s7_fitted, aes(index, resm_std, color = gender, shape = race)) +
  geom_point()

 b7<- ggplot(autism_s7_fitted, aes(interaction(gender, race), resc_std)) +
  geom_boxplot() +
  ylab("Standardised conditional residuals") +
  theme()


c7 <- ggplot(autism_s7_fitted, aes(sample = resc_std)) +
  geom_qq() +
  geom_qq_line(color = "red")

d7 <- ggplot(autism_s7_lcr, aes(sample = resmcp)) +
  geom_qq() +
  geom_qq_line(color = "red")

```

# set 4


```{r}

autism_set8 <- median_noise(0.4)

age8 <- ggplot(autism_set8, aes(age2, log10(y))) +
  geom_point() +
  facet_wrap_paginate(~childid, nrow = 5, ncol = 5, page = 1) +
  geom_smooth(method = "lm", se = F)+
  ggtitle("40%")

gender8 <- ggplot(autism_set8, aes(gender, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("40%")

racegen8 <- ggplot(autism_set8, aes(interaction(gender, race), y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("40%")

sic8 <- ggplot(autism_set8, aes(sicdegp, y, fill = race)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("40%")

best8 <- ggplot(autism_set8, aes(bestest2, y)) +
  geom_boxplot() +
  scale_y_log10()+
  ggtitle("40%")



```

```{r}
autism_s8_mod <- lmer(y ~ age2 + sicdegp + race + bestest2 + (age2 - 1 | childid) + (I(age2^2) - 1 | childid), data = autism_set8)
autism_s8_fitted <- autism_extract_fitted_mod(autism_s8_mod, autism_set8)
autism_s8_lcr <- autism_extract_lcr_mod(autism_s8_mod, autism_set8)
```

# Data plots

```{r}
a8 <- ggplot(autism_s8_fitted, aes(index, resm_std, color = gender, shape = race)) +
  geom_point()+
  

b8<- ggplot(autism_s8_fitted, aes(interaction(gender, race), resc_std)) +
  geom_boxplot() +
  ylab("Standardised conditional residuals") +
  theme()


c8 <- ggplot(autism_s8_fitted, aes(sample = resc_std)) +
  geom_qq() +
  geom_qq_line(color = "red")

d8 <- ggplot(autism_s8_lcr, aes(sample = resmcp)) +
  geom_qq() +
  geom_qq_line(color = "red")
```



```{r}
# change in median 

age1+age2+age3+age4
racegen1+racegen2+racegen3+racegen4
gender1+gender2+gender3+gender4
sic1+sic2+sic3+sic4
best1+best2+best3+best4

```


```{r}
# change in observations

age5+age6+age7+age8
racegen5+racegen6+racegen7+racegen8
gender5+gender6+gender7+gender8
sic5+sic6+sic7+sic8
best5+best6+best7+best8

```



```{r}

#change in median 
a0+a1+ggtitle("20%")+
  a2+ggtitle("25%")+
  a3+ggtitle("30%")+
  a4+ggtitle("35%")
b0+b1+ggtitle("20%")+
  b2+ggtitle("25%")+
  b3+ggtitle("30%")+
  b4+ggtitle("35%")
c0+c1+ggtitle("20%")+
  c2+ggtitle("25%")+
  c3+ggtitle("30%")+
  c4+ggtitle("35%")
d0+d1+ggtitle("20%")+
 d2+ggtitle("25%")+
  d3+ggtitle("30%")+
  d4+ggtitle("35%")
```

```{r}
#change in observations
a0+a5+ggtitle("25%")+
  a6+ggtitle("30%")+
  a7+ggtitle("35%")+
  a8+ggtitle("40%")
b0+b5+ggtitle("25%")+
  b6+ggtitle("30%")+
  b7+ggtitle("35%")+
  b8+ggtitle("40%")
c0+c5+ggtitle("25%")+
  c6+ggtitle("30%")+
  c7+ggtitle("35%")+
  c8+ggtitle("40%")
d0+ylim(-6,7)+
  d5+ggtitle("25%")+ylim(-6,7)+
  d6+ggtitle("30%")+ylim(-6,7)+
  d7+ggtitle("35%")+ylim(-6,7)+
  d8+ggtitle("40%")+ylim(-6,7)
```


